Exploratory and descriptive analysis

### 2023-04-09 notebook/exploratory.qmd
Add collapsed bar chart

```{r load-packages-data, message=FALSE, warning=FALSE}
library(tidyverse)
library(targets)
library(here)
library(sf)
library(ggrepel)

@@

```{r province-count-distribution, warning=FALSE}
ggplot(ongo, aes(x = province_count)) +
  geom_histogram(binwidth = 1, size = 0.1, boundary = 0,
                 fill = clrs[6], color = "white") +
  labs(x = "Number of provinces ONGOs are registered in", y = "Count") +
  theme_ongo()
```

>>>>

```{r load-packages-data, message=FALSE, warning=FALSE}
library(tidyverse)
library(targets)
library(here)
library(sf)
library(ggrepel)
library(scales)

@@

```{r province-count-distribution, warning=FALSE}
ggplot(ongo, aes(x = province_count)) +
  geom_histogram(binwidth = 1, size = 0.1, boundary = 0,
                 fill = clrs[6], color = "white") +
  labs(x = "Number of provinces INGOs are authorized to work in", y = "Count") +
  theme_ongo()
```

```{r province-count-collapsed}
provinces_collapsed <- ongo |> 
  drop_na(province_count) |> 
  mutate(province_count = case_when(
    province_count == 1 ~ "1 province",
    province_count > 1 & province_count < 32 ~ "2–31 provinces",
    province_count == 32 ~ "32 provinces"
  ))

ggplot(provinces_collapsed, aes(x = province_count)) + 
  geom_bar(fill = clrs[6]) +
  scale_y_continuous(sec.axis = sec_axis(trans = ~ . / nrow(provinces_collapsed),
                                         labels = label_percent())) +
  labs(x = "Number of provinces INGOs are authorized to work in", y = "Count") +
  theme_ongo()
```
